%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Elena Cossu}{Cossu}

\position{Senior Evaluation Researcher}
\address{London, United Kingdom}

\email{\href{mailto:elena.cossu@live.it}{\nolinkurl{elena.cossu@live.it}}}
\homepage{elenacossu.quarto.pub}
\github{elenacossu}
\linkedin{elenacossu}
\twitter{elle\_cossu}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {December, 2023}
    {Elena Cossu Cossu~~~·~~~coverletter}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{cover-letter}{%
\section{Cover Letter}\label{cover-letter}}

Dear Hiring Manager,

I am writing you this letter to apply for the Senior Evaluation Officer
(Quantitative/Economist) position. Let me briefly address your questions
below.

\emph{1) Why do you want to work at Foundations?}

I am applying for the Senior Evaluation Officer (Economist) because I
want to use my extensive academic and applied evaluation knowledge to
work for a place that makes a real difference in people's life.

As a professional, I am willing to build a research career for
organizations that aim at working for the social good. I believe that
the Foundations would be the perfect place to do so.

I also want to work with the leaders in the evaluation field and further
improve my knowledge as a quasi-experiment expert. During my experience
at the National Centre for Social Research I came to realise that the
Foundations are one of them, as we had multiple experience to work with
this organization.

\emph{2) How you believe your skills and experience will provide
specific value in relation to the essential and desirable criteria
outlined in the job description/role profile?}

I believe my skills and experience will provide further high-quality
knowledge and professionalism to the team. These skills would come from
my most recent working experiences as a Senior Evaluation Researcher for
the National Centre for Social Research and as a Postdoctoral
Researchers at SciencesPo, which is one of the leading European
universitied in applied social science research. Furthermore, I also
have experience from my role as a Early Stage Researcher at the European
Commission and my PhD in Economics.

For what concerns my skills, I have extensive experience in leading the
day-to-day delivery of quantitative evaluations for a charity thanks to
my Senior Research job at the National Centre for Social Research. As a
member of the Evaluation team, where I work on a daily basis with
creative and driven evaluators aiming to measure policies and
interventions

Also in this position I oversaw multiple externally commissioned
evaluations, from clients that include the UK Ministry of Justice, The
National Lottery Community Fund, the UK Department for Education, the
Education Endowment Foundation, the Department for Health and Social
Care (DHSC), and others.

I have research writing experience for what concerns feasibility
studies, reports, and academic publications. I wrote and published a
feasibility most recently in 2023, with the title `LNK Educate:
Feasibility and pilot study'. This feasibility study was for the Lives
not Knives evaluation, where I independently used and reported on
propensity score matching to see the effect of the intervention. The LNK
evaluation measures the effect of targeted tutoring on lives crime
attitudes among kids in targeted schools.

At NatCen I also gained experience in designing Randomised Controlled
Trials (RCT), most recently by designing the RCT for an evaluation
called `Send me a Pic' (SMAP), which is a two-arms randomised trial
measuring the effect of targeted tutoring on nude-image sharing
awareness.

I also have extensive experience in quasi-experiments, from matching to
Synthetic Control, gained through my PhD but as well through my
experience at NatCen. I published an academic paper that measured the
effect of policies on GDP growth in Hungary as part of my PhD
dissertation. I also have an overall high-level track record of academic
publications.

At NatCen I also wrote multiple bid to get new projects, most recently
on a project that uses Natural Language Processing to evaluate the
sentiment text of disability-related documents.

Last but not least, I have vast experience in working with different
kind of dataset, gained through all my work experiences as a researcher,
but in the evaluation sector as a researcher directly working on the
ELSA dataset. ELSA, `the English Longitudinal Study of Ageing', is one
of the longest lasting survey in the UK, and it provides a lot of skills
as a data manager working on it. I am also confident in using R, Python,
and a variety of other languages and related software to conduct
high-level data management and data analysis.

Thank you for considering my application. I look forward to the
possibility of discussing how my qualifications and experiences align
with the needs of What Works Centre for Children \& Families in more
detail. Please feel free to contact me at
\href{mailto:elena.cossu@live.it}{\nolinkurl{elena.cossu@live.it}} or
+33 6 95 10 79 67 to schedule an interview.

Sincerely,

Elena



\end{document}
